% Created 2010-10-10 Sun 18:28
\documentclass[presentation]{beamer}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{soul}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
\usepackage[english]{babel} \usepackage{ae,aecompl}
\usepackage{mathpazo,courier,euler} \usepackage[scaled=.95]{helvet}
\usepackage{listings}
\lstset{language=Python, basicstyle=\ttfamily\bfseries,
commentstyle=\color{red}\itshape, stringstyle=\color{darkgreen},
showstringspaces=false, keywordstyle=\color{blue}\bfseries}
\providecommand{\alert}[1]{\textbf{#1}}

\title{Parsing Data}
\author{FOSSEE}
\date{}

\usetheme{Warsaw}\usecolortheme{default}\useoutertheme{infolines}\setbeamercovered{transparent}
\begin{document}

\maketitle









\begin{frame}
\frametitle{Outline}
\label{sec-1}

\begin{itemize}
\item What is meant by parsing data?
\item String operations required for parsing
\item Converting between data-types.
\end{itemize}
\end{frame}
\begin{frame}
\frametitle{Question 1}
\label{sec-2}

  Split the variable line using a space as argument. Is it same as
  splitting without an argument ?
\end{frame}
\begin{frame}
\frametitle{Solution 1}
\label{sec-3}

  We see that when we split on space, multiple whitespaces are not
  clubbed as one and there is an empty string everytime there are two
  consecutive spaces.
\end{frame}
\begin{frame}
\frametitle{Question 2}
\label{sec-4}

  What happens to the white space inside the sentence when it is
  stripped? 
\end{frame}
\begin{frame}[fragile]
\frametitle{Solution 2}
\label{sec-5}

\lstset{language=Python}
\begin{lstlisting}
In []: a_str = "     white      space     "
In []: a_str.strip()
\end{lstlisting}
\end{frame}
\begin{frame}
\frametitle{Question 3}
\label{sec-6}

  What happens if you do \texttt{int("1.25")}
\end{frame}
\begin{frame}[fragile]
\frametitle{Solution 3}
\label{sec-7}

  It raises an error since converting a float string into integer
  directly is not possible. It involves an intermediate step of
  converting to float.
\lstset{language=Python}
\begin{lstlisting}
In []: dcml_str = "1.25"
In []: flt = float(dcml_str)
In []: flt
In []: number = int(flt)
In []: number
\end{lstlisting}
\end{frame}
\begin{frame}
\frametitle{Summary}
\label{sec-8}

\begin{itemize}
\item How to tokenize a string using various delimiters
\item How to get rid of extra white space around
\item How to convert from one type to another
\item How to parse input data and perform computations on it
\end{itemize}
\end{frame}
\begin{frame}
\frametitle{Thank you!}
\label{sec-9}

  \begin{block}{}
  \begin{center}
  This spoken tutorial has been produced by the
  \textcolor{blue}{FOSSEE} team, which is funded by the 
  \end{center}
  \begin{center}
    \textcolor{blue}{National Mission on Education through \\
      Information \& Communication Technology \\ 
      MHRD, Govt. of India}.
  \end{center}  
  \end{block}
\end{frame}

\end{document}
